Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-04-05 nb_px_paper/nb_body_text.tex
Broke Nb(p,x) paper into container w/ separate body text, appendices, and abstract, to be included in dissertation.  Still compiles into equivalent final PDF.

% % ****** Start of file apssamp.tex ******
% %
% %   This file is part of the APS files in the REVTeX 4.1 distribution.
% %   Version 4.1r of REVTeX, August 2010
% %
% %   Copyright (c) 2009, 2010 The American Physical Society.
% %
% %   See the REVTeX 4 README file for restrictions and more information.
% %
% % TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% % as well as the rest of the prerequisites for REVTeX 4.1
% %
% % See the REVTeX 4 README file
% % It also requires running BibTeX. The commands are as follows:
% %
% %  1)  latex apssamp.tex
% %  2)  bibtex apssamp
% %  3)  latex apssamp.tex
% %  4)  latex apssamp.tex
% %
% \documentclass[%
%  reprint,
% superscriptaddress,
% onecolumn,
% linenumbers,
% notitlepage,
% %groupedaddress,
% %unsortedaddress,
% %runinaddress,
% %frontmatterverbose, 
% %preprint,
% %showpacs,preprintnumbers,
% %nofootinbib,
% %nobibnotes,
% %bibnotes,
%  amsmath,amssymb,
%  aps,
% prc,
% %prb,
% %rmp,
% %prstab,
% %prstper,
% %floatfix,
% ]{revtex4-1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Important note on usage                  %%
%% -----------------------                  %%
%% This file must be compiled with PDFLaTeX %%
%% Using standard LaTeX will not work!      %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
% \documentclass[5p]{elsarticle}
% Good for final formatting  - two column
% 
% \documentclass[3p,times]{elsarticle}
% Final formatting
\documentclass[3p]{elsarticle}
% Good for proofing - single column
%

\usepackage[american]{babel}
\usepackage{amsmath}
\usepackage[version=3]{mhchem} 
% \usepackage{fixltx2e}
% \usepackage{refcount}
% \usepackage{siunitx}
% \usepackage{lastpage}
% \usepackage{textcomp}
\usepackage{mathtools}

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
\usepackage{listings}
\usepackage{mcode}
\usepackage [autostyle, english = american]{csquotes}
% \usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

% \usepackage{mathtools, cuted}

% \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage[section]{placeins}
\usepackage{multirow}

\usepackage{lineno}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\lstset{basicstyle=\small\ttfamily,columns=fullflexible}

% \usepackage{verbatim}

% \usepackage{gensymb}
% \usepackage{enumerate}
% \usepackage{float}
% \usepackage{bm}
% \usepackage{csquotes}
% \usepackage{mathtools}
% \usepackage[sort&compress]{natbib}
% \usepackage{biblatex}

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}

%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

%% Give the name of the journal
\journalname{Nuclear Instruments and Methods in Physics Research B}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{A.S. Voyles et al.}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{nimb}
% \jid{yspmi}

%% Give a short journal name for the dummy logo (if needed)
\jnltitlelogo{Nucl Instrum Meth B}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

\biboptions{sort&compress}

% if you have landscape tables
\usepackage[figuresright]{rotating}

% put your own definitions here:
%   \newcommand{\cZ}{\cal{Z}}
%   \newtheorem{def}{Definition}[section]
%   ...

% add words to TeX's hyphenation exception list
%\hyphenation{author another created financial paper re-commend-ed Post-Script}

% declarations for front matter

\usepackage{fancyvrb}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\footnotesize,        % size of fonts used for the code
  breaklines=true,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
}

% Sin and Cos with auto-parentheses 
\newcommand{\sinp}[1]{\sin{\left( #1\right)}}
\newcommand{\cosp}[1]{\cos{\left( #1\right)}}
\newcommand{\expp}[1]{\exp{\left( #1\right)}}
\newcommand{\sinhp}[1]{\sinh{\left( #1\right)}}
\newcommand{\lnp}[1]{\ln{\left( #1\right)}}
\newcommand{\pp}[1]{\left( #1\right)}
\newcommand{\sci}[2]{ #1 \cdot 10^{#2}\ }
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\norm}[1]{\lVert #1 \rVert}

\newcommand{\textred}[1]{\textcolor{red}{ #1}}
\newcommand{\redactedit}[1]{\textcolor{blue}{ \sout{#1}}}

\newcommand{\cmmnt}[1]{}

\newcommand{\colornote}[1]{\textcolor{red}{ COMMENT\large\footnote{\textcolor{red}{#1}}}}

\newcommand{\comment}[1]{\todo[color=blue!20!white,inline]{ASV: #1}}

\newcommand{\etal}{\emph{et\,al.}}

% Tweak sim for better inline text tilde
\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}

\sisetup{separate-uncertainty=true,table-space-text-post = *}

\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}

% \newcounter{subfigure}[figure]

\newcommand{\subfigimg}[4][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{#4pt}\raisebox{\dimexpr\ht1-2\baselineskip}{#2}}% Print label
  \phantom{\usebox1}% Insert appropriate spcing
}
% \subfigimg[scale=0.59]{a)}{./figures/after_minimization_plot_alt.pdf}{80pt}

\makeatletter
% Make common definition of mean
\newcommand*\mean[1]{\overline{#1\raisebox{3mm}{}}}

\makeatother

\begin{document}

\begin{frontmatter}

%\preprint{APS/123-QED}

% \title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}% Force line breaks with \\
% % \thanks{A footnote to the article title}%
% 
% \author{Andrew S. Voyles}
%  \email{andrew.voyles@berkeley.edu}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }% 
% \author{Lee A. Bernstein}
% \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }%
% \author{Eva R. Birnbaum}
% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
% \author{Jonathan W. Engle}
%  \email{jwengle@wisc.edu}
% \affiliation{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
% \author{Stephen A. Graves}
% \affiliation{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
% \author{Toshihiko ??? Kawano}
% \affiliation{Nuclear Physics Group, Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
% %  \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
% \author{Amanda M. Lewis}%
% % \author{Eric F. Matthews}%
% %  \email{Second.Author@institution.edu}
% \affiliation{%
%  Department of Nuclear Engineering, University of California, Berkeley, Berkeley, CA 94720, USA
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% }%
% \author{Francois M. Nortier}
% \affiliation{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory, Los Alamos, NM 87544, USA}

% \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
\author[ucb]{Andrew S. Voyles \corref{cor1}}
\ead{andrew.voyles@berkeley.edu}

% \author[lbl]{M.S. Basunia}
% 
% \author[ucb]{J.C. Batchelder}
%

\author[lbl,ucb]{Lee A. Bernstein}

\author[lanl]{Eva R. Birnbaum}

\author[uwm]{Jonathan W. Engle}
\ead{jwengle@wisc.edu}

\author[iowa]{Stephen A. Graves}

\author[tlanl]{Toshihiko  Kawano}

\author[ucb]{Amanda M. Lewis}

\author[lanl]{Francois M. Nortier}

\address[ucb]{Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\address[lbl]{Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA}
% \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
\address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison,  Madison, WI 53705, USA}
\address[lanl]{Isotope Production Facility, Chemistry Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}
\address[iowa]{Department of Radiation Oncology, University of Iowa,  Iowa City, IA 52242, USA}
\address[tlanl]{Theoretical Division, Los Alamos National Laboratory,  Los Alamos, NM 87544, USA}

% % \collaboration{MUSO Collaboration}%\noaffiliation
% % 
% % \author{Charlie Author}
% % %  \homepage{http://www.Second.institution.edu/~Charlie.Author}
% % \affiliation{
% %  Second institution and/or address\\
% %  This line break forced% with \\
% % }%
% % \affiliation{
% %  Third institution, the second for Charlie Author
% % }%
% % \author{Delta Author}
% % \affiliation{%
% %  Authors' institution and/or address\\
% %  This line break forced with \textbackslash\textbackslash
% % }%
% % 
% % \collaboration{CLEO Collaboration}%\noaffiliation
% 
% \date{\today}% It is always \today, today,
%              %  but any date may be explicitly specified
% 
% %% Title, authors and addresses
% 
% %% use the tnoteref command within \title for footnotes;
% %% use the tnotetext command for the associated footnote;
% %% use the fnref command within \author or \address for footnotes;
% %% use the fntext command for the associated footnote;
% %% use the corref command within \author for corresponding author footnotes;
% %% use the cortext command for the associated footnote;
% %% use the ead command for the email address,
% %% and the form \ead[url] for the home page:
% %%
\title{Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb}

%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

% \dochead{Short}
%% Use \dochead if there is an article header, e.g. \dochead{Short communication}

% 
% % \author[rvt]{C.V. ̃Radhakrishnan\corref{cor1}\fnref{fn1}}
% \author[ucb]{Andrew S. Voyles \corref{cor1}}
% \ead{andrew.voyles@berkeley.edu}
% 
% % \author[lbl]{M.S. Basunia}
% % 
% % \author[ucb]{J.C. Batchelder}
% 
% 
% \author[ucb,lbl]{Lee A. Bernstein}
% 
% 
% \author[lanl]{Eva R. Birnbaum}
% 
% \author[uwm]{Jonathan W. Engle}
% 
% \author[iowa]{Stephen A. Graves}
% 
% \author[ucb]{Amanda M. Lewis}
% 
% 
% \author[lanl]{Francois M. Nortier}

% \author[ucb]{M.A. Unzueta}
% 
% \author[ucb]{K.A. van Bibber}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

% \cortext[cor1]{Corresponding author}
% \cortext[cor2]{Principal corresponding author}
% \fntext[fn1]{This is the specimen author footnote.}
% \fntext[fn2]{Another author footnote, but a little more longer.}

% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, Etcheverry Hall, 2521 Hearst Ave, Berkeley, CA 94709}
% \address[lbl]{Lawrence Berkeley National Laboratory,  1 Cyclotron Rd, Berkeley, CA 94720}
% \address[llnl]{Lawrence Livermore National Laboratory, 7000 East Ave, Livermore, CA 94550}

% \address[ucb]{Department of Nuclear Engineering, University of California, Berkeley, 4155 Etcheverry Hall, MC 1730, Berkeley, CA 94720, USA}
% \address[lbl]{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd., Berkeley, CA 94720, USA}
% % \address[llnl]{Lawrence Livermore National Laboratory, Livermore CA, 94551 USA}
% \address[uwm]{Department of Medical Physics, University of Wisconsin -- Madison, 1111 Highland Ave., Madison, WI 53705, USA}
% \address[lanl]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87544, USA}
% \address[iowa]{Department of Radiation Oncology, University of Iowa, 200 Hawkins Drive, Iowa City, IA 52242, USA}

\begin{abstract}

% Intermediate-energy proton beams are used to produce a wide range of radionuclides for use in medical treatments and research.  
% However, reaction modeling in this energy range remains largely untested, and there is a paucity of monitor reactions in this energy range needed to establish beam characteristics  for quantitative cross section measurements.  
% To address this need, a
A stack  of thin Nb 
% , Cu, and Al monitor 
foils was irradiated with the 100 MeV proton beam at  Los Alamos National Laboratory's Isotope Production Facility,  to investigate the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} nuclear reaction as a  monitor for intermediate energy proton experiments and to benchmark state-of-the-art reaction model codes.
% A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
% The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new monitor reaction standard for intermediate-energy protons.
A set of 38 measured  cross sections for  \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40--90 MeV, as well as 5 independent measurements of isomer branching ratios, are reported. 
% The measurements are 
These are useful in medical and basic science radionuclide productions at intermediate energies. 
% Cross sections were measured using the well-characterized 
The
% \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, 
\ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn}  reactions were used to
determine proton fluence, and all activities were quantified using HPGe spectrometry.
Variance minimization techniques were employed to reduce systematic uncertainties in proton energy and fluence, improving the reliability of these measurements. 
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with improved precision compared with previous measurements.
This work also reports the first measurement of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, and of the independent cross sections for    
% \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, 
\ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn} and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40--90 MeV region.
% \textred{
% Due to \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination  by  activation of the silicone adhesive used for sealing foil packets, the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na}  monitor reactions  were excluded, in the interest of surety, from proton fluence determination.
% }
% \textred{
% To avoid inadvertently reporting enhanced proton fluence due to
The effects of  \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} contamination, arising from  silicone adhesive in the Kapton tape used to encapsulate the aluminum monitor foils, is also discussed as a cautionary note to future stacked-target cross section measurements.
% strongly discouraged.
% }
% Comparisons against the 
\emph{A priori} predictions of the reaction modeling codes  CoH, EMPIRE, and TALYS are compared with experimentally measured values and used to explore the differences between codes for the
% impact of pre-equilibrium particle emission  for the 
% 40--90 MeV 
\ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.

% \begin{description}
% \item[Usage]
% Secondary publications and information retrieval purposes.
% \item[PACS numbers]
% May be entered using the \verb+\pacs{#1}+ command.
% \item[Structure]
% You may use the \texttt{description} environment to structure your abstract;
% use the optional argument of the \verb+\item+ command to give the category of each item. 
% \end{description}
\end{abstract}

% \pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired

% \begin{abstract}

% \end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium 
% \sep Copper\sep Aluminum 
\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
% Proton activation \sep 
% Proton transport \sep 
Stacked target activation \sep Monitor reactions \sep 
% Monitor foils 
Medical isotope production \sep Isomer branching ratios \sep  
% Nuclear spin distributions  \sep 
MCNP \sep  LANL
% 
% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)
% 
\end{keyword}

\end{frontmatter}

% \maketitle

%%
%%  To-do list for comments
%%
% \listoftodos

%%
%% Start line numbering here if you want
%%
\linenumbers

@@

including intense and distinct gamma-rays, 

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[width=\linewidth]{a)}{./figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_minimization}
    \end{subfigure}%
     \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=\linewidth]{b)}{./figures/after_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_minimization}
    \end{subfigure}%
    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%. A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions. Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
     \label{fig:variance_mins}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[width=\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:Na22_activity_compare}
    \end{subfigure}%
     \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:Na24_activity_compare}
    \end{subfigure}%
    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections. At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up. \ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
     \label{fig:Na_activity_compare}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \subfigimg[width=\linewidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         \refstepcounter{subfigure}\label{fig:before_subtraction}
    \end{subfigure}%
     \begin{subfigure}[t]{0.50\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=\linewidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         \refstepcounter{subfigure}\label{fig:after_subtraction}
    \end{subfigure}%
    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets. Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.  By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
     \label{fig:na_subtraction}
\end{figure}

@@

 \section{Acknowledgements}

%  Stephen Graves - consulting for methodology, guidance.

 The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.

We gratefully acknowledge support for this work from the United States Department of Energy, Office of Science via the Isotope Development and Production for Research and Applications subprogram in the Office of Nuclear Physics. 
This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory and the U.S. Nuclear Data Program under contract \# DE-AC02-05CH11231.
This research was performed under appointment to the Rickover Fellowship Program in Nuclear Engineering, sponsored by the Naval Reactors Division of the U.S. Department of Energy
Additional support has been provided by the U.S. Nuclear Regulatory Commission.

This research used the Savio computational cluster resource provided by the Berkeley Research Computing program at the University of California, Berkeley (supported by the UC Berkeley Chancellor, Vice Chancellor for Research, and Chief Information Officer).

%  This work has been carried out at the University of California, Berkeley, and performed under the auspices of the U.S. Department of Energy by Lawrence Livermore National Laboratory under contract \# DE-AC52-07NA27344 and Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
% Funding has been provided from the US Nuclear Regulatory Commission, the US Nuclear Data Program, the Berkeley Geochronology Center, NSF ARRA Grant \# EAR-0960138, the University of California Laboratory Fees Research Grant \# 12-LR-238745, and  DFG Research Fellowship \# RU 2065/1-1.

% This work has been carried out  under the auspices of the U.S. Department of Energy by  Lawrence Berkeley National Laboratory under contract \# DE-AC02-05CH11231.
% Funding has been provided from the US Nuclear Regulatory Commission and the US Nuclear Data Program.

%  \comment{Please provide me here with all relevant contract / grant / fellowship / funding ID numbers, as well as anyone else that you feel should be acknowledged here.}

>>>>

@@

including intense, distinct gamma-rays, 

@@

% \begin{figure*}
%     \centering
%     \subfloat{
%         \centering
% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \subfigimg[width=0.5\textwidth]{a)}{./figures/336keV_curve_new.pdf}{50}
% %         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
% %          \refstepcounter{subfloat}
%          \label{fig:decay_curve_336}
% %          
%          \subfigimg[width=0.5\textwidth]{b)}{./figures/391keV_curve_new.pdf}{50}
% %         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
% %          \refstepcounter{subfloat}
%          \label{fig:decay_curve_391}
%     }%

\begin{figure}
    \centering
    \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/before_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:before_minimization}
   \hspace{-5pt}}%
     \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_minimization_plot.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:after_minimization}
   \hspace{-5pt}}%
    \caption{Results of variance minimization through enhancement of the effective areal density of the 6061 aluminum degraders by 2.52\%. A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions. Following minimization, additional apparent fluence is observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, due to contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets.}
     \label{fig:variance_mins}
\end{figure}

\begin{figure}
    \centering
    \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \hspace{-5pt}\subfigimg[width=0.5\linewidth]{a)}{./figures/Na22_activity_compare.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
%          \label{fig:Na22_activity_compare}
   \hspace{-5pt}}%
     \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=0.5\linewidth]{b)}{./figures/Na24_activity_compare.pdf}{180}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:Na24_activity_compare}
   \hspace{-5pt}}%
    \caption{Estimates of EoB \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} and \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} activities using TENDL-2015 cross sections, in comparison with the IAEA recommended \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} cross sections. At low energies, experimentally observed apparent \ce{^{22,24}Na} activities in each Al foil packet are consistent with IAEA recommendations, but diverge at higher energies as the \ce{^{nat}Si}(p,x)\ce{^{22}Na} exit channels begin to open up. \ce{^{22,24}Na} activities consistent with TENDL-2015 estimates are observed in each Nb and Cu foil packet as well, confirming that contamination may be attributed to activation of silicone adhesives.}
     \label{fig:Na_activity_compare}
\end{figure}

@@

\begin{figure}
    \centering
    \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \hspace{-5pt}\subfigimg[width=0.5\textwidth]{a)}{./figures/after_minimization_plot_alt.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:before_subtraction}
   \hspace{-5pt}}%
     \subfloat{
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[scale=0.6]{./figures/391keV_curve2.png}
        \subfigimg[width=0.5\textwidth]{b)}{./figures/after_subtraction_plot.pdf}{80}
%         \caption{ Decay curve for the isomeric transition of \ce{^{113m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:after_subtraction}
   \hspace{-5pt}}%
    \caption{The \enquote{extra fluence} observed in the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels is caused by contamination from \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} on the silicone adhesive used for sealing foil packets. Following subtraction of \ce{^{22,24}Na} activities observed in the silicone adhesive of Nb and Cu foils in the same energy \enquote{compartment}, the consistency of the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction improves  dramatically.  By excluding these contaminated channels, the remaining 3 independent monitor reactions serve to minimize uncertainty in stack energy assignments and incident fluence.}
     \label{fig:na_subtraction}
\end{figure}

@@
